Fixing Vulnerabilities Hinders Maintainability

### 2020-01-27 paper/icpc20.tex
results

	\item \textbf{Miscellaneous (674 cases)} This pattern comprises
		several other security refactorings that do not have a CWE assigned and patterns that
		do not satisfy the Wilcoxon test size requirement of more than $20$ refactorings.

@@

\begin{enumerate}
\item Diff comparison between the security patch commit (\emph{sha}) and its parent(\emph{sha-p}).
\item Selects a random commit from the security patch project (\emph{sha-reg}).
\item Diff comparison between the random commit (\emph{sha-reg}) and its parent (\emph{sha-reg-p}).
\item Check if the size from the regular change has the same/approximated size to 
the security patch.
\end{enumerate}

@@

\begin{figure}[H]	
 	\centering 	\includegraphics[width=0.46\textwidth]{figures/maintainability_sec_vs_reg.pdf}
 	\caption{Maintainability difference for security and baseline patches}
	\label{fig:secvsreg}

@@

\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.57\textwidth]{figures/impact_per_guideline.pdf}
 	\caption{Impact of a security patch in 8 out of the 10 guidelines.}
	\label{fig:guidelines}

@@

\begin{figure}[H]
 	\centering
 	\includegraphics[width=0.5\textwidth]{figures/maintainability_severity.pdf}
 	\caption{Maintainability difference by the vulnerabilities severity.}
	\label{fig:severity}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/maintainability_language.pdf}
  \caption{Maintainability difference by language after security patches.}
  \label{fig:lang_main}  
\end{figure}

>>>>

	\item \textbf{Miscellaneous (673 cases)} This pattern comprises
		several other security refactorings that do not have a CWE assigned and patterns that
		do not satisfy the Wilcoxon test size requirement of more than $20$ refactorings.

@@

\begin{enumerate}
\item Diff comparison between the security patch commit (\emph{sha}) and its parent (\emph{sha-p}).
\item Selects a random commit from the security patch project (\emph{sha-reg}).
\item Diff comparison between the random commit (\emph{sha-reg}) and its parent (\emph{sha-reg-p}).
\item Check if the size from the regular change has the same/approximated size to 
the security patch.
\end{enumerate}

@@

\begin{figure}[h]	
 	\centering 	\includegraphics[width=0.46\textwidth]{figures/maintainability_sec_vs_reg.pdf}
 	\caption{Maintainability difference for security and baseline patches.}
	\label{fig:secvsreg}

@@

\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.5\textwidth]{figures/impact_per_guideline.pdf}
 	\caption{Impact of the security patches for each guideline.}
	\label{fig:guidelines}
	\scalebox{0.5}{
	\begin{tabular}{r@{: }l r@{: }l}
	$WCC$ & Write Clean Code & $KACB$ & Keep Architecture Components Balanced\\
	$CACL$ & Couple Architecture Components Loosely & $SCM$ & Separate Concerns in Modules \\
	$KUIS$ & Keep Unit Interfaces Small & $WCO$ & Write Code Once \\
	$WSimpleUC$ & Write Simple Units of Code & $WShortUC$ & Write Short Units of Code
	\end{tabular}
	}
\end{figure}

Maintainability is being calculated as the mean of the guidelines computed
by BCH. Figure~\ref{fig:guidelines} shows the impact of security patches on each 
guideline individually. For projects with large 
codebases, the results retrieved for \emph{Keep Your Codebase Small} were not 
viable due to limitations of BCH. Thus, we decided to not consider this guideline 
in our analysis.
Regarding the impact of security patches in each guideline, we observe
that overall our patches have a significant positive impact in $5$ guidelines: 
\emph{Write Clean Code} (p-value = $4.9$x$10^{-54}$), \emph{Keep Architecture 
Components Balanced} (p-value = $5.26$x$10^{-71}$), \emph{Couple Architecture 
Components Loosely} (p-value = $2.43$x$10^{-07}$), \emph{Keep Unit Interfaces 
Small} (p-value = $2.25$x$10^{-13}$), \emph{ Write Code Once} (p-value = 
$7.9$x$10^{-35}$). However, each of the previous guidelines also suffer a negative 
impact from $10\%$ to $35\%$. \emph{Separate Concerns in Module} guideline also follows the same results but without any statistical significance since the p-value is higher than $0.05$. According with the results, \emph{Write Simple Units of Code} (p-value=$0.015$ and $38.2\%$/$396$ of negative cases) and \emph{Write Short Units of Code} (p-value=$0.029$ and $38.3\%$/$397$ of negative cases) are the guidelines which suffered more impact from security patches.

\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.5\textwidth]{figures/maintainability_severity.pdf}
 	\caption{Maintainability difference by the vulnerabilities severity.}
	\label{fig:severity}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/maintainability_language.pdf}
  \caption{Maintainability difference by language after security patches.}
  \label{fig:lang_main}  
\end{figure}
